---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tgppt

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/tgppt)](https://CRAN.R-project.org/package=tgppt)
[![Travis build status](https://travis-ci.com/tanaylab/tgppt.svg?branch=master)](https://travis-ci.org/tanaylab/tgppt)
[![Codecov test coverage](https://codecov.io/gh/tanaylab/tgppt/branch/master/graph/badge.svg)](https://codecov.io/gh/tanaylab/tgppt?branch=master)
<!-- badges: end -->

The goal of tgppt is to provide handy functions to plot directly to powerpoint in R.

## Installation

You can install tgppt with:

``` r
remotes::install_github("tanaylab/tgppt")
```

## Example

Plot base R directly to a powerpoint presentation:

```{r base_example}
library(tgppt)
temp_ppt <- tempfile(fileext = ".pptx")
plot_base_ppt({plot(mtcars$mpg, mtcars$drat)}, temp_ppt)
```

Plot ggplot to a powerpoint presentation:

```{r gg_example}
library(tgppt)
library(ggplot2)
gg <- ggplot(mtcars, aes(x=mpg, y=drat)) + geom_point()
temp_ppt <- tempfile(fileext = ".pptx")
plot_gg_ppt(gg, temp_ppt)
```

Create a new powerpoint file: 
```{r new_file}
library(tgppt)
new_ppt("myfile.pptx")
```

Use "Arial" font based ggplot theme: 
```{r arial}
ggplot2::theme_set(theme_arial(8))
```

## Note on plotting a large number of points

Powerpoint might crash when plotting a large number of points, so it is advised to use the a rasterized version of geom_point:

```{r geom_point_rast}
library(tgppt)
library(ggplot2)
gg <- ggplot(mtcars, aes(x=mpg, y=drat)) + geom_point_rast()
temp_ppt <- tempfile(fileext = ".pptx")
plot_gg_ppt(gg, temp_ppt)
```

The same problem might occur when plotting a boxplot with many outliers:

```{r geom_boxplot_jitter}
library(tgppt)
library(ggplot2)
gg <- ggplot(mtcars, aes(x=factor(cyl), y=drat)) + geom_boxplot_jitter()
temp_ppt <- tempfile(fileext = ".pptx")
plot_gg_ppt(gg, temp_ppt)
```





